Reviving stochasticity: eccentricity convergence depends on black hole binary orbit

### 2023-04-19 papers/paper-eccentricity/paper-eccentricity.tex
Set up directory for eccentricity paper

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[BAGGinS-I]{Bayesian Analysis of Gas-free Galaxies in Simulations I: Reviving Stochasticity}

@@

% Abstract of the paper
\begin{abstract}
We present the Bayesian Analysis of Gas-free Galaxies in Simulations (BAGGinS) project, show that stochasticity is ubiquitous with collisionless merger sims.
\end{abstract}

@@

\input{./sections/stats}

@@

\input{sections/appendix}

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Reviving Stochasticity]{Reviving stochasticity: eccentricity convergence depends on black hole binary orbit}

@@

% Abstract of the paper
\begin{abstract}
We present some stuff about eccentricity convergence in Nbody sims
\end{abstract}

@@

@@

%\input{sections/appendix}
